---
title: "AkatoreA_Network"
output: html_document
date: "2023-08-1"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(igraph)
library(readxl)
library(dplyr)
library(ggplot2)
library(kableExtra)
```


```{r}
data2 <- read_xls("AkatoreA.xls")
```

Reference [24] 
Reference [25]
```{r}
dd1 <- as.data.frame(data2)
rownames(dd1) <- dd1[, 1]
dd1 <- dd1[, -c(1)]
gg2 <- graph_from_adjacency_matrix(as.matrix(dd1), mode = "directed")
```

Number of nodes and edges

```{r}
vcount(gg2) #no.of vertices
ecount(gg2) #no.of edges
```
Shortest Paths

```{r}
# The diameter function gives the longest shortest path in the network.
diameter(gg2, directed = TRUE, unconnected = TRUE, weights=NA)
diameter(gg2, directed = FALSE, unconnected = TRUE, weights=NA)

```


```{r}
# This function gives the pair of nodes with longest shortest path between them in the network
far2_und <- farthest_vertices(gg2,directed = FALSE, weights=NA)
far2_und
# This function gives the pair of nodes with longest shortest path between them in the network
far2_dir <- farthest_vertices(gg2,directed = TRUE, weights=NA)
far2_dir
```

```{r}
from_node <- far2_und$vertices[1]
to_node <-far2_und$vertices[2]

short.path2<-shortest_paths(gg2, from = from_node, to = to_node, weights = NA, mode="all", output = "both")
short.path2$vpath

from_node <- far2_dir$vertices[1]
to_node <-far2_dir$vertices[2]

short.path21<-shortest_paths(gg2, from = from_node, to = to_node, weights = NA, mode="all", output = "both")
short.path21$vpath

```


Clustering coefficient

```{r}
cat("clustering coefficient :", transitivity(gg2, type="localaverage"))
```

Average path length

```{r}
cat("average path length :", mean_distance(gg2))
```

```{r}

```


```{r}
dgCmat2<- as_adjacency_matrix(gg2)
gg_mat2 <- as.matrix(dgCmat2)
gg_mat2 %>%
  kbl(caption = "Ythan_Estuary Food Web Matrix") %>%
  kable_styling(full_width = F)%>%
  scroll_box(width = "850px", height = "300px")
```


The number of species
```{r}
number_of_species2 <-ncol(gg_mat2)
results2 <- data.frame(Measure="Number of Species",
                  Value=number_of_species2,
                  stringsAsFactors=FALSE)
results2
```

```{r}
gg_layout <- layout_with_lgl(gg2)
# plot the graph
plot(gg2, 
layout=gg_layout,
vertex.color= rgb(0.3,0.9,0.1, 0.6),
vertex.size= 8, 
vertex.frame.color=NA, 
vertex.label.color="black", 
vertex.label.cex=0.5, 
vertex.label.dist=0, 
edge.curved=0.2,
edge.width=0.4,
edge.arrow.size=0.01,
edge.color= rgb(0.5,0.5,0.5, 0.3),
main="AkatoreA Network")

```

The number of predators for each species

```{r}
row_count2<- rowSums(gg_mat2)
row_count_df2 <-as.data.frame(row_count2)
colnames(row_count_df2) <- "predators"
row_count_df2$Species<-rownames(row_count_df2)
rownames(row_count_df2)<-NULL
row_count_df2<-row_count_df2[,c("Species","predators")]
row_count_df2 %>%
  arrange(-`predators`)%>% 
  kbl(caption = "Number of predators for each species") %>%
  kable_styling(full_width = F)%>%
  scroll_box( height = "400px")
```


The number of prey species eaten by each species

```{r}
col_count2<-colSums(gg_mat2)
col_count_df2 <-as.data.frame(col_count2)
colnames(col_count_df2)<- c("prey")
col_count_df2$Species<-rownames(col_count_df2)
rownames(col_count_df2)<-NULL
col_count_df2<-col_count_df2[,c("Species","prey")]
col_count_df2  %>%
  arrange(-`prey`)%>%
  kbl(caption = "Number of prey species eaten by each species") %>%
  kable_styling(full_width = F)%>%
  scroll_box( height = "400px")
```


Basal species

```{r}
basal2 <- c()
b_count2<-0
for(i in 1:length(col_count2)){
  if(col_count2[i] == 0 ){
    b_count2 = b_count2 + 1
    basal2<-c(basal2,names(col_count2)[i])
  }
}
basal_df2 <- as.data.frame(basal2)
colnames(basal_df2)<-"Basal species"
kbl(basal_df2) %>%
  kable_styling(full_width = F)%>%
  scroll_box( height = "300px")
```

Top species

```{r}
top2 <- c()
t_count2<-0
for(i in 1:length(row_count2)){
  if(row_count2[i] == 0 ){
    t_count2 = t_count2 + 1
    top2<-c(top2,names(row_count2)[i])
  }
}
top_df2 <- as.data.frame(top2)
colnames(top_df2)<-"Top species"
kbl(top_df2) %>%
  kable_styling(full_width = F)%>%
  scroll_box( height = "300px")
```

Intermediate species

```{r}
i_count2 <- number_of_species2 - (t_count2 + b_count2)
species<-rownames(gg_mat2)
intermediate2<-species[! (species %in% basal2 | species %in% top2) ]
intermediate_df2 <- as.data.frame(intermediate2)
colnames(intermediate_df2)<-"Intermediate species"
kbl(intermediate_df2) %>%
  kable_styling(full_width = F)%>%
  scroll_box( height = "300px")
```

Ratio of prey to predators


```{r}
prey_ratio2 <- round((b_count2 + i_count2)/(i_count2 +t_count2),1)
results2<-rbind(results2, c("Ratio of Prey to Predators ", prey_ratio2))
print(results2)
```

Number of Predations

```{r}
num_predations2 <- sum(gg_mat2)
results2<-rbind(results2, c("Number of Predations ", num_predations2))
```

Connectance

```{r}
all_possible_links2 = number_of_species2 *  (number_of_species2-1)
connectance2<- round(num_predations2/all_possible_links2,2)
results2<-rbind(results2, c("Connectance", connectance2))

```

Number of cannibals

```{r}
c_count2<-0
for(i in 1:number_of_species2){
  if(gg_mat2[i,i]!=0){
    c_count2=c_count2+1
  }
}
results2<-rbind(results2, c("Number of Cannibals", c_count2))

```

Predators with single prey species

```{r}
freq_of_one2 <- table(col_count2)[["1"]]
results2<-rbind(results2, c("Number of predators with single prey species", freq_of_one2))
print(results2)
```


Degree Centrality

In-degree

```{r}
in_deg2<-degree(gg2, mode="in")
cat(paste0("Highest in-degree="), max(in_deg2),"\n")
which(in_deg2==max(in_deg2))

```
Out-degree

```{r}
out_deg2<-degree(gg2, mode="out")
cat(paste0("Highest out-degree="), max(out_deg2),"\n")
which(out_deg2==max(out_deg2))
```
```{r}
deg_cent2<-degree(gg2)
cat(paste0("Degree centrality="), max(deg_cent2),"\n")
which(deg_cent2==max(deg_cent2))
```
Betweenness Centrality

```{r}
bet_cent2 <- betweenness(gg2, weights = NA)
bet_cent2
cat(paste0("Betweenness centrality="),max(bet_cent2),"\n")
which.max(bet_cent2)
```

Closeness centrality

```{r}
close_cent2<- closeness (gg2, mode="out", normalized = T)
cat(paste0("Closeness centrality"),"\n")
which.max(close_cent2)
```


```{r}
GnBlRe4<-c("#C7E9B4", "#2C7FB8", "#62b357","#CC4C02")
ylGnBl5<-c("#FFFFCC","#C7E9B4","#7FCDBB","#40B6C4","#2C7FB8" ,"#253494")
GnBlRe<-colorRampPalette(GnBlRe4)
fine = 20
lyt <- layout_with_dh(gg2)
```

```{r}
graphCol2 = GnBlRe(fine)[as.numeric(cut(deg_cent2,breaks = fine))]
plot(gg2, vertex.color = graphCol2, main = "Degree Centrality", vertex.label.cex = 0.5, 
     layout = lyt[, 2:1], vertex.size = 8, edge.arrow.size = 0.3, edge.width = 0.5, edge.curved = 0.1, 
     vertex.frame.color = "white", vertex.label.color = "black")
```


```{r}
graphCol2 = GnBlRe(fine)[as.numeric(cut(bet_cent2,breaks = fine))]
plot(gg2, vertex.color = graphCol2, main = "Betweenness Centrality", vertex.label.cex = 0.5, 
     layout = lyt[, 2:1], vertex.size = 8, edge.curved = 0.1, edge.arrow.size = 0.3, edge.width = 0.5,
     vertex.frame.color = "white", vertex.label.color = "black")


```

```{r}


```

Delete an edge to see if we can shift the centrality focus to the right side of the graph

```{r}
graphCol2 = GnBlRe(fine)[as.numeric(cut(deg_cent2,breaks = fine))]
gg_sp2<-delete.vertices(gg2, "Unidentified detritus")
gg_sp2<-plot(gg_sp2, vertex.color = graphCol2, main = "Degree Centrality After removing Unidentified detritus", vertex.label.cex = 0.5, 
     layout = lyt[, 2:1], edge.arrow.size = 0.3, vertex.size = 8, edge.curved = 0.1, 
     vertex.frame.color = "white", vertex.label.color = "black", edge.width = 0.5)
```



```{r}
graphCol2 = GnBlRe(fine)[as.numeric(cut(bet_cent2,breaks = fine))]
gg_sp2<-delete.vertices(gg2, "Deleatidium (N=15)")
gg_sp2<-plot(gg_sp2, vertex.color = graphCol2, main = "Betweenness Centrality After removing Deleatidium (N=15)", vertex.label.cex = 0.5, 
     layout = lyt[, 2:1], edge.arrow.size = 0.3, vertex.size = 8, edge.curved = 0.1, 
     vertex.frame.color = "white", vertex.label.color = "black", edge.width = 0.5)
```



```{r}
graphCol2 = GnBlRe(fine)[as.numeric(cut(close_cent2,breaks = fine))]
gg_sp2<-delete.vertices(gg2, "Unidentified detritus")
gg_sp2<-plot(gg_sp2, vertex.color = graphCol2, main = "Closeness Centrality After removing Unidentified detritus", vertex.label.cex = 0.5, 
     layout = lyt[, 2:1], edge.arrow.size = 0.5, vertex.size = 10, edge.curved = 0.1, 
     vertex.frame.color = "white", vertex.label.color = "black", edge.width = 0.5)
```

Population A: Top species
Population B: Intermediate species
Population C: Basal species


When a portion of B is removed:

```{r}
# Function to simulate the agent-based model
simulate_agent_based_model <- function(num_generations, 
                                       initial_pop_A, initial_pop_B, initial_pop_C,
                                       birth_rate_A, birth_rate_B, birth_rate_C,
                                       death_rate_A, death_rate_B, death_rate_C,
                                       consumption_AB, consumption_BC, consumption_C,
                                       removal_ratio_A, removal_ratio_B, removal_ratio_C) {
  
  # Create empty data frame to store results
  model_results <- data.frame(Generation = numeric(),
                              Population_A = numeric(),
                              Population_B = numeric(),
                              Population_C = numeric())
  
  # Initialize populations
  population_A <- initial_pop_A
  population_B <- initial_pop_B
  population_C <- initial_pop_C

  total_resources <- population_A + population_B + population_C
  
  # Simulation loop for each generation
  for (generation in 1:num_generations) {
    # Compute resource consumed by each species
    resource_consumed_AB <- consumption_AB * population_B/total_resources
    resource_consumed_BC <- consumption_BC * population_C/total_resources
    resource_consumed_C <- consumption_C * population_C/total_resources
    
    # Update populations based on birth, death rates, and resource consumption
    new_population_A <- population_A + (birth_rate_A * population_A * resource_consumed_AB) - (death_rate_A * population_A)
    new_population_B <- population_B + (birth_rate_B * population_B * resource_consumed_BC) - (death_rate_B * population_B)
    new_population_C <- population_C + (birth_rate_C * population_C * resource_consumed_C) - (death_rate_C * population_C )
    
    # If removal_ratio is specified, remove a percentage of each species' population
    if (!is.null(removal_ratio_A)) {
      removal_count_A <- round(initial_pop_A * removal_ratio_A)
      new_population_A <- max(new_population_A - removal_count_A, 0)
    }
    
    if (!is.null(removal_ratio_B)) {
      removal_count_B <- round(initial_pop_B * removal_ratio_B)
      new_population_B <- max(new_population_B - removal_count_B, 0)
    }
    
    if (!is.null(removal_ratio_C)) {
      removal_count_C <- round(initial_pop_C * removal_ratio_C)
      new_population_C <- max(new_population_C - removal_count_C, 0)
    }
    
    # Update populations for the next generation
    population_A <- max(round(new_population_A), 0)
    population_B <- max(round(new_population_B), 0)
    population_C <- max(round(new_population_C), 0)
    
    # Store the results for this generation
    model_results <- rbind(model_results, c(generation, population_A, population_B, population_C))
  }
  
  colnames(model_results) <- c("Generation", "Population_A", "Population_B", "Population_C")
  return(model_results)
}

# Parameters for the simulation
num_generations <- 50
initial_pop_A <- 100 * t_count2 # Number of top species 
initial_pop_B <- 1000 * i_count2  # Number of intermediate species
initial_pop_C <- 6000 * b_count2 # Number of basal species (prey)
birth_rate_A <- 0.2
birth_rate_B <- 0.4
birth_rate_C <- 0.8
death_rate_A <- 0.05
death_rate_B <- 0.1
death_rate_C <- 0.2
consumption_AB <- 0.2  # Resource consumption rate of predators (B) by top predators (A)
consumption_BC <- 0.3  # Resource consumption rate of prey (C) by intermediate species (B)
consumption_C <- 0.1 #Resource consumption rate of sunlight, plants etc by prey (C)
removal_ratio_A <- 0  # Proportion of top predator's population to remove
removal_ratio_B <- 0.2  # Proportion of predator's population to remove
removal_ratio_C <- 0  # Proportion of prey's population to remove

# Run the simulation
results <- simulate_agent_based_model(num_generations, 
                                      initial_pop_A, initial_pop_B, initial_pop_C,
                                      birth_rate_A, birth_rate_B, birth_rate_C,
                                      death_rate_A, death_rate_B, death_rate_C,
                                      consumption_AB, consumption_BC, consumption_C,
                                      removal_ratio_A, removal_ratio_B, removal_ratio_C)

# Print the results
print(results)
 results$Population_A[results$Population_A <= 0] <- 1  # Set zero or negative values to 1
 results$Population_B[results$Population_B <= 0] <- 1
 results$Population_C[results$Population_C <= 0] <- 1

# Plot the results with improved aesthetics
ggplot(results, aes(x = Generation)) +
  geom_line(aes(y = Population_A, color = "Population_A"), size = 0.8) +
  geom_line(aes(y = Population_B, color = "Population_B"), size = 0.8) +
  geom_line(aes(y = Population_C, color = "Population_C"), size = 0.8) +
  labs(x = "Generation", y = "Population", color = "Species") +
  scale_x_continuous(breaks = seq(0, num_generations, by = 10)) +  # Custom x-axis breaks
  scale_y_log10(labels = scales::comma) +
  #scale_y_continuous(trans = "log10", breaks = c(100, 1000, 10000, 100000)) +
  #scale_y_continuous(breaks = seq(0, 10000)) +  # Custom y-axis breaks
  scale_color_manual(values = c("Population_A" = "blue", "Population_B" = "red", "Population_C" = "green"))+
  theme_minimal() +
  theme(legend.title = element_blank(),  
        legend.position = "right")

```
When a portion of A is removed:

```{r}
# Function to simulate the agent-based model
simulate_agent_based_model <- function(num_generations, 
                                       initial_pop_A, initial_pop_B, initial_pop_C,
                                       birth_rate_A, birth_rate_B, birth_rate_C,
                                       death_rate_A, death_rate_B, death_rate_C,
                                       consumption_AB, consumption_BC, consumption_C,
                                       removal_ratio_A, removal_ratio_B, removal_ratio_C) {
  
  # Create empty data frame to store results
  model_results <- data.frame(Generation = numeric(),
                              Population_A = numeric(),
                              Population_B = numeric(),
                              Population_C = numeric())
  
  # Initialize populations
  population_A <- initial_pop_A
  population_B <- initial_pop_B
  population_C <- initial_pop_C
  
  total_resources <- population_A + population_B + population_C
  
  # Simulation loop for each generation
  for (generation in 1:num_generations) {
    # Compute resource consumed by each species
    resource_consumed_AB <- consumption_AB * population_B/total_resources
    resource_consumed_BC <- consumption_BC * population_C/total_resources
    resource_consumed_C <- consumption_C * population_C/total_resources
    
    # Update populations based on birth, death rates, and resource consumption
    new_population_A <- population_A + (birth_rate_A * population_A * resource_consumed_AB) - (death_rate_A * population_A)
    new_population_B <- population_B + (birth_rate_B * population_B) - (death_rate_B * population_B * resource_consumed_BC)
    new_population_C <- population_C + (birth_rate_C * population_C * resource_consumed_C) - (death_rate_C * population_C)
    
    # If removal_ratio is specified, remove a percentage of each species' population
    if (!is.null(removal_ratio_A)) {
      removal_count_A <- round(initial_pop_A * removal_ratio_A)
      new_population_A <- max(new_population_A - removal_count_A, 0)
    }
    
    if (!is.null(removal_ratio_B)) {
      removal_count_B <- round(initial_pop_B * removal_ratio_B)
      new_population_B <- max(new_population_B - removal_count_B, 0)
    }
    
    if (!is.null(removal_ratio_C)) {
      removal_count_C <- round(initial_pop_C * removal_ratio_C)
      new_population_C <- max(new_population_C - removal_count_C, 0)
    }
    
    # Update populations for the next generation
    population_A <- max(round(new_population_A), 0)
    population_B <- max(round(new_population_B), 0)
    population_C <- max(round(new_population_C), 0)
    
    # Store the results for this generation
    model_results <- rbind(model_results, c(generation, population_A, population_B, population_C))
  }
  
  colnames(model_results) <- c("Generation", "Population_A", "Population_B", "Population_C")
  return(model_results)
}

# Parameters for the simulation
num_generations <- 50
initial_pop_A <- 100 * t_count2 # Number of top species 
initial_pop_B <- 1000 * i_count2  # Number of intermediate species
initial_pop_C <- 6000 * b_count2 # Number of basal species (prey)
birth_rate_A <- 0.2
birth_rate_B <- 0.3
birth_rate_C <- 0.8
death_rate_A <- 0.05
death_rate_B <- 0.15
death_rate_C <- 0.2
consumption_AB <- 0.2  # Resource consumption rate of predators (B) by top predators (A)
consumption_BC <- 0.15  # Resource consumption rate of prey (C) by intermediate species (B)
consumption_C <- 0.1 #Resource consumption rate of sunlight, plants etc by prey (C)
removal_ratio_A <- 0.1  # Proportion of top predator's population to remove
removal_ratio_B <- 0  # Proportion of predator's population to remove
removal_ratio_C <- 0  # Proportion of prey's population to remove

# Run the simulation
results <- simulate_agent_based_model(num_generations, 
                                      initial_pop_A, initial_pop_B, initial_pop_C,
                                      birth_rate_A, birth_rate_B, birth_rate_C,
                                      death_rate_A, death_rate_B, death_rate_C,
                                      consumption_AB, consumption_BC, consumption_C,
                                      removal_ratio_A, removal_ratio_B, removal_ratio_C)

# Print the results
print(results)
results$Population_A[results$Population_A <= 0] <- 1  # Set zero or negative values to 1
results$Population_B[results$Population_B <= 0] <- 1
results$Population_C[results$Population_C <= 0] <- 1

# Plot the results with improved aesthetics
ggplot(results, aes(x = Generation)) +
  geom_line(aes(y = Population_A, color = "Population_A"), size = 0.8) +
  geom_line(aes(y = Population_B, color = "Population_B"), size = 0.8) +
  geom_line(aes(y = Population_C, color = "Population_C"), size = 0.8) +
  labs(x = "Generation", y = "Population", color = "Species") +
  scale_x_continuous(breaks = seq(0, num_generations, by = 10)) +  # Custom x-axis breaks
  scale_y_log10(labels = scales::comma) +
  scale_color_manual(values = c("Population_A" = "blue", "Population_B" = "red", "Population_C" = "green"))+
  theme_minimal() +
  theme(legend.title = element_blank(),  
        legend.position = "right")
```
Here we can see that, as 10% of the population A is removed, the growth of population B is increasing as it doesn't have a predator and the prey of it, population C is decreasing. 

```{r}


```

When Portion of C is removed: 
```{r}
# Function to simulate the agent-based model
simulate_agent_based_model <- function(num_generations, 
                                       initial_pop_A, initial_pop_B, initial_pop_C,
                                       birth_rate_A, birth_rate_B, birth_rate_C,
                                       death_rate_A, death_rate_B, death_rate_C,
                                       consumption_AB, consumption_BC, consumption_C,
                                       removal_ratio_A, removal_ratio_B, removal_ratio_C) {
  
  # Create empty data frame to store results
  model_results <- data.frame(Generation = numeric(),
                              Population_A = numeric(),
                              Population_B = numeric(),
                              Population_C = numeric())
  
  # Initialize populations
  population_A <- initial_pop_A
  population_B <- initial_pop_B
  population_C <- initial_pop_C
  
  total_resources <- population_A + population_B + population_C
  
  # Simulation loop for each generation
  for (generation in 1:num_generations) {
    # Compute resource consumed by each species
    resource_consumed_AB <- consumption_AB * population_B/total_resources
    resource_consumed_BC <- consumption_BC * population_C/total_resources
    resource_consumed_C <- consumption_C * population_C/total_resources
    
    # Update populations based on birth, death rates, and resource consumption
    new_population_A <- population_A + (birth_rate_A * population_A * resource_consumed_AB) - (death_rate_A * population_A)
    new_population_B <- population_B + (birth_rate_B * population_B * resource_consumed_BC) - (death_rate_B * population_B)
    new_population_C <- population_C + (birth_rate_C * population_C * resource_consumed_C) - (death_rate_C * population_C)
    
    # If removal_ratio is specified, remove a percentage of each species' population
    if (!is.null(removal_ratio_A)) {
      removal_count_A <- round(initial_pop_A * removal_ratio_A)
      new_population_A <- max(new_population_A - removal_count_A, 0)
    }
    
    if (!is.null(removal_ratio_B)) {
      removal_count_B <- round(initial_pop_B * removal_ratio_B)
      new_population_B <- max(new_population_B - removal_count_B, 0)
    }
    
    if (!is.null(removal_ratio_C)) {
      removal_count_C <- round(initial_pop_C * removal_ratio_C)
      new_population_C <- max(new_population_C - removal_count_C, 0)
    }
    
    # Update populations for the next generation
    population_A <- max(round(new_population_A), 0)
    population_B <- max(round(new_population_B), 0)
    population_C <- max(round(new_population_C), 0)
    
    # Store the results for this generation
    model_results <- rbind(model_results, c(generation, population_A, population_B, population_C))
  }
  
  colnames(model_results) <- c("Generation", "Population_A", "Population_B", "Population_C")
  return(model_results)
}

# Parameters for the simulation
num_generations <- 50
initial_pop_A <- 100 * t_count2 # Number of top species 
initial_pop_B <- 1000 * i_count2  # Number of intermediate species
initial_pop_C <- 6000 * b_count2 # Number of basal species (prey)
birth_rate_A <- 0.1
birth_rate_B <- 0.15
birth_rate_C <- 0.5
death_rate_A <- 0.05
death_rate_B <- 0.1
death_rate_C <- 0.2
consumption_AB <- 0.4  # Resource consumption rate of predators (B) by top predators (A)
consumption_BC <- 0.2  # Resource consumption rate of prey (C) by intermediate species (B)
consumption_C <- 0.1 #Resource consumption rate of sunlight, plants etc by prey (C)
removal_ratio_A <- 0  # Proportion of top predator's population to remove
removal_ratio_B <- 0  # Proportion of predator's population to remove
removal_ratio_C <- 0.5  # Proportion of prey's population to remove

# Run the simulation
results <- simulate_agent_based_model(num_generations, 
                                      initial_pop_A, initial_pop_B, initial_pop_C,
                                      birth_rate_A, birth_rate_B, birth_rate_C,
                                      death_rate_A, death_rate_B, death_rate_C,
                                      consumption_AB, consumption_BC, consumption_C,
                                      removal_ratio_A, removal_ratio_B, removal_ratio_C)

# Print the results
print(results)
results$Population_A[results$Population_A <= 0] <- 1  # Set zero or negative values to 1
results$Population_B[results$Population_B <= 0] <- 1
results$Population_C[results$Population_C <= 0] <- 1

# Plot the results with improved aesthetics
ggplot(results, aes(x = Generation)) +
  geom_line(aes(y = Population_A, color = "Population_A"), size = 0.8) +
  geom_line(aes(y = Population_B, color = "Population_B"), size = 0.8) +
  geom_line(aes(y = Population_C, color = "Population_C"), size = 0.8) +
  labs(x = "Generation", y = "Population", color = "Species") +
  scale_x_continuous(breaks = seq(0, num_generations, by = 10)) +  # Custom x-axis breaks
  scale_y_log10(labels = scales::comma) +
  scale_color_manual(values = c("Population_A" = "blue", "Population_B" = "red", "Population_C" = "green"))+
  theme_minimal() +
  theme(legend.title = element_blank(),  
        legend.position = "right")
```


```{r}

```

```{r}

```

```{r}


```

```{r}

```


